\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-11-07 report/sdc_report.tex
tidy; rm old files
tidy, rm big files

% Make header in inkscape?
\begin{figure}[width=\textwidth]
\vspace{-3em}
\centering
\includegraphics[width=.7\textwidth]{Figures/header2.pdf}
\vspace{.5em}
\end{figure}

@@

I analysed the {\bf London house prices} dataset in several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights to enable
data-driven investment decisions.

A full report with additional interactive visualisations is online at {\bf
  \leavevmode\href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \leavevmode\href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

{\let\thefootnote\relax\footnotetext{\textsuperscript{1} \textit{MRC
      Human Genetics Unit, University of Edinburgh, Scotland, United Kingdom}}}

@@

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes, and
how have they changed over time? A real estate professional can
give an opinion based on their own limited sample size, but with a
large dataset we can address these questions quantitatively and
visualise the results.

@@

Letting and sales sites may currently list some recent sales, but it's
not currently possible to see a quantitative overview of property
prices in a region, within the context of its sector, district and
postcode.

%\setlength{\intextsep}{0em}
\begin{wrapfigure}[16]{l}{.45\textwidth}
\vspace{.5em}
\centering
\includegraphics[width=.43\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
%\vspace{35em}
\end{wrapfigure}

@@

These questions can be answered with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- we
call this the fractal context of a property price (Figure 1).

A specific postcode or area can be marked within its distribution,
giving a clear view of a properties relative pricing which cannot be
gleaned just by browsing recent sales. The example view (Figure 1)
combines ranked violin density plots and a geo-heatmap for a clear,
intuitive view of a locations price context.

@@

Given a time series of housing prices, it's of interest to investors
to speculate on potential investment returns for a given property
area. This can be done through time series analysis using the
autoregressive integrated moving average (ARIMA) model (Figure 2). The
model fitting procedure included regularisation that allowed a $drift$
term to model non-stationary trends, as well as coefficients capturing
periodicity or seasonal effects. Potential investment returns could be
optimised by selecting areas with
maximal growth projections. \\

@@

Combining growth forecasts and other derived metrics from this
dataset allow an approximate investment grading, relative to other
postcodes within the area covered by this dataset. This intuitive
output metric can help prioritise areas ripe for property investment.

As an example, Figure 3 shows the top 5 postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include Brockley,
whose train station within SE4 1 was linked with the London Overground network in 2010.\\

@@

Growth forecasts and volatility were converted to quantiles and
weighted equally; those sectors with the highest projected growth
and least historical volatility receive the best investment grade
(on a scale of AAA, AA, A, BBB \ldots C).\textsuperscript{$\star$}

Returning to our original example, SW18 4HU is a promising choice of
area for property investment. It's median-priced for the sector, which
is the cheapest of SW18 (in turn part of the desirable SW London area;
Figure 1). It has good growth projections of over £28,000 in the next
year (Figure 2), and receives the top AAA investment grade, being
in the 90\textsuperscript{th} percentile for predicted price growth
and low historical volatility in the dataset.

{\let\thefootnote\relax\footnotetext{\textsuperscript{$\star$}
    Data intended to assist investors and does not constitute
    investment advice; independent advice should be sought where appropriate. }}

@@

There are currently no mainsteam property sales or rental sites that
attempts to provide any quantitative insights to contextualise a
property's list price. Some list recent nearby sales in plain text,
but the wealth of historical sales data available allows for much
richer displays (as demonstrated with the fractal context view,
\emph{above}), which offer valuable and practical insights to
prospective homebuyers.

This added feature would help differentiate a given sales and letting
site as well as increase the brand positioning of \logo\hspace{.1em}
within the real estate sector. Contextual maps could be drawn as
interactive D3.js visualisations and neatly integrated with a typical
property search. Additionally, web analytics data from our partnered
site could be fed-back to help further enhancement and expansion of
the data-driven insights and visualisations we offer.

@@

\logo \hspace{.1em} would release both a {\bf web service} and associated
{\bf mobiles and tablet applications}. These would offer limited analysis and
visualisation without any fee, with collected user data and feedback helping to
validate the business model and develop our software.

\begin{wrapfigure}[12]{r}{.4\textwidth}
\centering
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
%\vspace{-1em}
\end{wrapfigure}

Releasing these products aligns with our aims of democratising real
estate investment. Amateur property investors and prospective
landlords can make data-driven decisions, the likes of which are likely
already employed by large investment trusts and funds.

A small data science team will gradually expand the range of analyses
offered, integrating novel public and privately-acquired datasets and
release them under a rolling subscription model, aimed at private
landlords and property speculators, as well as professional real
estate investment trusts (REITs). Significant revenue could be
generated through tailored partnerships with funds and high net-worth
individuals.

@@

Having established a property area analytics brand, \logo\hspace{.1em}
will look to develop business relationships with real estate
investment funds and high net-worth individuals as a {\bf quantitative
  property investment consultancy} and independent analyst for the
financial services. Our domain expertise and existing partnerships and
products would place us as a market leader in this undeveloped
segment.

@@

\begin{wrapfigure}[10]{r}{.3\textwidth}
\vspace{2em}
\centering
\includegraphics[width=.2\textwidth]{Figures/logo.png}
\includegraphics[width=.2\textwidth]{Figures/logotext.png}
%\caption*{ {\sf Democratising real estate investment}}
\caption{ Logo design. }
%\vspace{-4em}
\end{wrapfigure}

In this report I've given a brief overview my attempts to elute
maximal insight from a single large dataset through visualisations and
quantitative modelling. Together these form a cohesive narrative of
investigative analysis into a single exemplar postcode, and discovery
of the potential investment returns therein.

These analyses have the potential to generate valuable insights for a range of
customer segments:
\begin{itemize}

@@

\vspace{1em}
\begin{flushright} {\small An enhanced online version of this short
    report is available at:
    \leavevmode\href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}

>>>>

\begin{figure}[width=\textwidth]
\vspace{-3em}
\centering
\includegraphics[width=.7\textwidth]{Figures/header2.pdf}
\vspace{.5em}
\end{figure}

@@

I analysed the {\bf London house prices} dataset in several creative
ways. Firstly, the \emph{fractal context} of an area visualises how house
prices relate to those of neighbouring areas at different scales up
and down the postcode hierarchy. Secondly, I fit \emph{ARIMA models}
to forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, growth and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights to
enable data-driven investment decisions.

An enhanced report with interactive visualisations is online at 
{\bf \leavevmode\href{http://blm.io/datarea}{blm.io/datarea} } 
and scripts to reproduce all analyses are available from 
{\bf
  \leavevmode\href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}
}.

@@

%{\let\thefootnote\relax\footnotetext{\textsuperscript{1} \textit{MRC
 %     Human Genetics Unit, University of Edinburgh, Scotland, United Kingdom}}}

@@

When considering a property in a given area, you may want to ask
questions like: how do prices here compare to the surrounding areas?
How have they changed over time? Where will they be in a year's time?
A real estate professional can give an opinion based on their own
limited sample size, but with a large dataset we can address these
questions through statistical analysis and visualise the results.

@@

Letting and sales sites sometimes list some recent sales in a given
area, but it's not currently possible to get a quantitative overview
of property prices in a region, within the context of its sector,
district and postcode.

%\setlength{\intextsep}{0em}
\begin{wrapfigure}[16]{l}{.45\textwidth}
%\vspace{.5em}
\centering
\includegraphics[width=.43\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
%\vspace{35em}
\end{wrapfigure}

@@

These questions can be answered with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- what
I've called the fractal context of a property price (Figure 1).

Any chosen area can be seen in the context of its surroundings, from
full postcodes to much wider areas, clearly showing how the pricing of
any given property relates to those nearby.  The example graphic for
postcode SW18 4HU (Figure 1) combines ranked violin density plots and
a geo-heatmap for a clear, intuitive view of a location's price
context.

@@

Property investors need a method of evaluating the potential investment
returns of a given property area. This can be achieved through time
series modelling with autoregressive integrated moving average (ARIMA)
models (Figure 2). For this application regularised models were fit
which allowed a $drift$ term to capture non-stationary trends
(i.e. allowing for gain, loss or neither) as well as coefficients
reflecting periodicity or seasonal effects. Hence potential investment
returns could then be optimised by selecting areas with
maximal growth projections.

@@

Combining growth forecasts and with an additional measure of
variability allows an approximate investment grading of each sector,
relative to other postcodes within the area covered by this
dataset. This intuitive output metric can help prioritise areas ripe
for property investment and combines the theoretical model projections
with an empirical metric of past stability.

As an example, Figure 3 shows the top 5 postcode sectors in which to
invest, according to their 12-month price growth forecast and
historical annualised volatility. These include Brockley,
whose train station within SE4 1 was linked with the London Overground network in 2010.\\

@@

Growth forecasts and volatility were converted to quantiles and
equally weighted (Figure 4); those sectors with the highest projected growth
and least historical volatility receive the best investment grade
(on a scale of AAA, AA, A, BBB \ldots C).

Returning to our original example, SW18 4HU is a promising choice of
area for property investment.\textsuperscript{$\star$} It's
median-priced for the sector, which is the cheapest of SW18 (in turn
part of the desirable SW London area; Figure 1). It has good growth
projections of over £28,000 in the next year (Figure 2), and receives
the top AAA investment grade for being in the 90\textsuperscript{th}
percentile for predicted price growth and low historical volatility
compared to all other sectors covered by the dataset.

{\let\thefootnote\relax\footnotetext{\textsuperscript{$\star$}
    Data intended to assist investors but does not constitute
    investment advice; independent investment advice should be sought where
    appropriate. The value of investments can go down as well as up. }}

@@

There are currently no mainsteam property sales or rental sites that
attempt to provide any quantitative insights that contextualise a
property's list price. Some list recent nearby sales in plain text,
but the wealth of historical sales data available allows for much
richer displays (as demonstrated with the fractal context view,
Section A: Figure 1, and by the interactive data-driven map shown in
Figure 5), which offer valuable and practical insights to prospective
homebuyers.

This added feature would help differentiate a given sales and letting
site as well as increase the brand positioning of \logo\hspace{.1em}
within the real estate sector. Contextual maps could be drawn as
interactive D3.js visualisations and neatly integrated with a typical
property search. Additionally, web analytics data from our partnered
site could be fed-back to help further enhancement and expansion of
the data-driven insights and visualisations we offer, such as how
often a given area is searched for on their site and by which
demographics.

@@

\logo \hspace{.1em} will release an initial product both as a {\bf web
  service} and associated {\bf mobiles and tablet applications}
(Figure 6). These
offer limited analysis and visualisation without any fee, with
collected user data and feedback helping to validate the business
model and futher develop our software.

\begin{wrapfigure}[14]{r}{.46\textwidth}
\vspace{.5em}
\centering
\includegraphics[width=.42\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
%\vspace{-1em}
\end{wrapfigure}

Releasing these products aligns with our aims of democratising real
estate investment. Amateur property investors and prospective
landlords can make data-driven decisions, the likes of which are 
already employed by analysts for large investment funds.

A small data science team will gradually expand the range of analyses
offered, integrating novel public and privately-acquired datasets and
release them to a premium app under a rolling subscription model,
aimed at private landlords and property speculators as well as
professional real estate investment trusts (REITs). Significant
revenue could be generated through tailored partnerships with funds
and high net-worth individuals.

@@

Having established a property area analytics brand, \logo\hspace{.1em}
will look to develop business relationships with real estate
investment funds and high net-worth individuals as a {\bf quantitative
  property investment consultancy} and independent analyst for the
financial services. Our domain expertise and existing partnerships and
products would place us as a market leader in this largely undeveloped
segment.

\begin{wrapfigure}[10]{l}{.33\textwidth}
\vspace{5em}
\centering
\includegraphics[width=.2\textwidth]{Figures/logo.png}
\includegraphics[width=.2\textwidth]{Figures/logotext.png}
%\caption*{ {\sf Democratising real estate investment}}
\caption{ Branding. }
%\vspace{-4em}
\end{wrapfigure}

@@

In this report I've given a brief overview my attempts to elute
maximal insight from a single large dataset through statistical
modelling, visualisations and other data science techniques. Together
these form a narrative of investigative analysis into a single
exemplar postcode, and the assessment of the potential investment
returns within.

I have shown that these analyses have the potential to generate
valuable insights for a range of customer segments:

\setitemize[0]{leftmargin=4em,itemindent=2em}
\begin{itemize}

@@

\vspace{2em}

\hrule

\vspace{1.5em}
%\begin{flushright}
\centering 
{\small An enhanced online version of this short
    report is available at:
    \leavevmode\href{http://blm.io/datarea}{blm.io/datarea}}
%\end{flushright}
